Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-04-07 publication_materials/ms_rbc.tex
formatting: new lines for sentences

\par Reduced models are often valuable when supplemented by direct simulation [source?]. Nonlinear simulations performed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling. Instead, the characteristic jet-like structure is somewhat present on initialization. This is practical because the convective transient period generally involves high-Reynolds number flows whose resolution is prohibitive. 
\section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. The equations of motion are then given by
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
where $p$ is pressure and $T$ is temperature. For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. Any system of this form can be characterized by its Rayleigh number $Ra$ and Prandtl number $Pr$, where $Ra$ is the timescale ratio of thermal diffusion to convection and $Pr$ is the ratio of momentum diffusivity to thermal diffusivity.  For convenience, we define 
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\par To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$). At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1.
Then the mean profiles are given by
    \mathbf{\bar{u}} &= \mathbf{0} \\
    \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
    \bar{p}(z) &= p_0 + \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
Accordingly, the fields are defined as
    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z) + p'(x, z, t).
Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
with Dirichlet boundary conditions 
    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant. Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. A complete linear stability analysis requires solution over the full spectrum of wavenumbers. The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.

\section{Temperature profile evolution}\label{sec:evolution}
For this investigation, we allow $ \bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
\begin{align}
    \frac{\partial \bar{T}}{\partial t} + \mathbf{u}' \cdot \nabla T' + \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' = \mathcal{P} \nabla^2 T' + \mathcal{P} \nabla^2 \bar{T}.
    \label{EQ:T't_xz}
\end{align}
Subtracting (\ref{EQ:linear3}) from (\ref{EQ:T't_xz}) eliminates several terms. We can replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}). Taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
\begin{align}
    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle
\end{align}
where $\langle \cdot \rangle$ denotes the horizontal average. The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$. The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations. For completeness, we provide the normalization 
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
\end{equation}
and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
\begin{equation}
    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
upon which the remainder of this investigation is centered. It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. We also assume this term is composed of eigenfunctions belonging to the dominant mode. 
\par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebshev polynomial basis. The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features. We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).
\par To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}. We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. This generally involves a unique and unknown value $A^2 > 0$. Our method of finding $A^2$ is best illustrated through example.

\begin{figure}[h]
    \includegraphics[width=3.4in]{EV_spectrum_ol.png}
    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0. Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). Advection tends to stabilize the system, decreasing its eigenvalues (shown in red). It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
    \label{fig:iteration_spectra} 
\end{figure}

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
Thermally equilibrated states of this kind are solutions to a particular quasilinear form of the Rayleigh-B\'enard convection equations. For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. Solutions are symmetric about $z = 0$ by design. This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonconstant horizontal velocity perturbations, as is the case in \cite{Waleffe}. 
\par Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging. The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues. Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.
\par The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. These dips appear in every solution, regardless of $Ra$. Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}. This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
\begin{figure}[h]
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. The initial profile is given by (\ref{EQ:T0}). The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. The simulation temperature data are horizontally- and time-averaged. The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. The purpose of this feature is not well understood.}
    \label{fig:T0_profiles}
\begin{figure}[h]
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$). The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\begin{figure*}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). Advection profiles belong to marginally-stable modes. For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
    \vspace{0.4in}
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}. Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}. Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$. $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. This is well illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
    \label{fig:del_inv}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
    \label{fig:bl_ra}
\end{figure}

@@

\par In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow. Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}. This is consistent with Malkus' marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.

@@

This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions

@@

which will hereby be referred to as the conductive initial condition. $t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. We define the equilibrated initial conditions

@@

% \begin{figure}[h]

@@

\begin{figure*}[t]
    \begin{minipage}[t]{3.4in}

>>>>

Reduced models are often valuable when supplemented by direct simulation [source?]. 
Nonlinear simulations performed with quasilinear solutions as initial conditions do not undergo a convective transient period of turbulent upwelling. 
Instead, the characteristic jet-like structure is somewhat present on initialization. 
This is practical because the convective transient period generally involves high-Reynolds number flows whose resolution is prohibitive.

\section{Conventional Boussinesq Linear Stability Analysis}\label{sec:boussinesq}
We begin with the non-dimensionalized Boussinesq approximation for Rayleigh-Bénard Convection. 
The domain is 2-dimensional rectangular and horizontally periodic with spatial dimensions $0 < x < 4$ and $-1/2 < z < 1/2$. 
The fluid of interest is constrained between two planar boundaries at $z = -1/2$ and $z = 1/2$ with fixed temperatures $1$ and $0$ respectively. 
At both boundaries we specify impenetrable, no-slip conditions, such that the velocity $\mathbf{u} = u \hat{x} + w \hat{z} = \mathbf{0}$ at $z = \pm 1/2$. 
The equations of motion are then given by
\begin{align}
    \nabla \cdot \mathbf{u} &= 0 \label{EQ:motion1}\\
    \frac{\partial \mathbf{u}}{\partial t} + \mathbf{u} \cdot \nabla \mathbf{u} &= - \nabla p + T \hat{z} + \sqrt{\frac{Pr}{Ra}} \nabla^2 \mathbf{u} \label{EQ:motion2}\\
    \frac{\partial T}{\partial t} + \mathbf{u} \cdot \nabla T &= \frac{1}{\sqrt{RaPr}} \nabla^2 T \label{EQ:motion3}
\end{align}
where $p$ is pressure and $T$ is temperature. 
For completeness, we specify a final boundary condition $p = p_0$ at $z = \pm 1/2$. 
Any system of this form can be characterized by its Rayleigh number $Ra$ and Prandtl number $Pr$, where $Ra$ is the timescale ratio of thermal diffusion to convection and $Pr$ is the ratio of momentum diffusivity to thermal diffusivity.  
For convenience, we define 
\begin{equation}
\mathcal{R} = \sqrt{\frac{Pr}{Ra}}, \qquad \mathcal{P} = \frac{1}{\sqrt{Pr Ra}}.
\end{equation}

To derive the linearized system, we posit that each field can be represented as the sum of a mean profile (denoted by $\bar{\cdot } \;$) and a perturbation function (denoted by $\cdot'$). 
At an arbitrary time $t_0$, suppose $\frac{\partial \bar{T}}{\partial z} (z)$ is some given function which satisfies
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \frac{\partial \bar{T}}{\partial z}\Big|_{t=t_0} dz = -1.
\end{equation}
Then the mean profiles are given by
\begin{align}
    \mathbf{\bar{u}} &= \mathbf{0} \\
    \bar{T}(z) &= 1 + \int_{-\frac{1}{2}}^{z} \frac{\partial \bar{T}}{\partial \zeta}\Big|_{t=t_0}(\zeta) d\zeta \\
    \bar{p}(z) &= p_0 + \int_{-\frac{1}{2}}^z \bar{T}\Big|_{t=t_0}(\zeta) d\zeta.
\end{align}
Accordingly, the fields are defined as
\begin{align}
    \mathbf{u}(x, z, t) &= \mathbf{u'}(x, z, t) \label{EQ:reynolds_dc_u}\\
    &= u'(x, z, t)\hat{x} + w'(x, z, t)\hat{z} \\
    T(x, z, t) &= \bar{T}(z) + T'(x, z, t) \label{EQ:reynolds_dc_T}\\
    p(x, z, t) &= \bar{p}(z) + p'(x, z, t).
\end{align}
Upon substitution, we equate terms which scale linearly with the perturbations, yielding the linearized stability equations
\begin{align}
    \nabla \cdot \mathbf{u'} &= 0 \label{EQ:linear1}\\
    \frac{\partial\mathbf{u'}}{\partial t} &= - \nabla p' + T'\hat{z} + \mathcal{R} \nabla^2 \mathbf{u'} \label{EQ:linear2}\\
    \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' &= \mathcal{P} \nabla^2 T' \label{EQ:linear3}
\end{align}
with Dirichlet boundary conditions 
\begin{equation}
    T'|_{z = \pm \frac{1}{2}} = 0, \quad u'|_{z = \pm \frac{1}{2}} = 0, \quad p'|_{z = \pm \frac{1}{2}} = 0.
\end{equation}
In 1916, Lord Rayleigh observed that (\ref{EQ:linear1}) and (\ref{EQ:linear3}) can be manipulated into a separable form with generalized solutions
\begin{align}
    w'(x, z, t) &= W(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes1}\\ 
    u'(x, z, t) &= U(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes2}\\ 
    T'(x, z, t) &= \theta(z) \, e^{i(k_xx-st)} \label{EQ:normal_modes3}\\ 
    p'(x, z, t) &= P(z) \, e^{i(k_xx-st)}\label{EQ:normal_modes4}
\end{align}
where $s = \sigma + i\omega$ and $k_x$ is constrained, by periodicity, to the countably infinite set (spectrum) of wavenumbers
\begin{align}
    k_x \in \big\{\frac{n\pi}{2} \, \big| \, n \in \mathbb{N}\big\}.
\end{align}
For each $k_x$, we can assess the stability of the perturbations by solving for the eigenvalue $s$, whose imaginary component $\omega$ plays the role of an exponential growth rate. 
Solution yields a finite set of eigenvalues, among which, that with maximum $\omega$ is assumed to be dominant. 
Positive eigenvalues indicate that the system is unstable to small disturbances of wavenumber $k_x$, while negative eigenvalues indicate stability. 
A complete linear stability analysis requires solution over the full spectrum of wavenumbers. 
The prototypical case is used to demonstrate that the critical Rayleigh number $Ra_c = 1708$ when $\frac{\partial \bar{T}}{\partial z} = -1$.

\section{Temperature profile evolution}\label{sec:evolution}
For this investigation, we allow $ \bar{T}$ to vary in $z$ and $t$. Substituting (\ref{EQ:reynolds_dc_T}) into (\ref{EQ:motion3}) yields
\begin{align}
    \frac{\partial \bar{T}}{\partial t} + \mathbf{u}' \cdot \nabla T' + \frac{\partial T'}{\partial t} + \frac{\partial \bar{T}}{\partial z} w' = \mathcal{P} \nabla^2 T' + \mathcal{P} \nabla^2 \bar{T}.
    \label{EQ:T't_xz}
\end{align}
Subtracting (\ref{EQ:linear3}) from (\ref{EQ:T't_xz}) eliminates several terms. 
We can replace the advective term $\mathbf{u}' \cdot \nabla T'$ with $\grad \cdot (\mathbf{u}'T')$ due to (\ref{EQ:linear1}). 
Taking the horizontal average of (\ref{EQ:T't_xz}), this advective term can be reduced to
\begin{align}
    \frac{1}{4}\int_0^4 \grad \cdot (\mathbf{u}'T') dx &= \frac{\partial }{\partial z}  \langle w'T' \rangle
\end{align}
where $\langle \cdot \rangle$ denotes the horizontal average. 
The remaining terms in (\ref{EQ:T't_xz}) are unaffected as they are independent of $x$. 
The eigenfunctions $W(z),\, U(z),\, \theta(z),$ and $P(z)$ do not admit any natural normalization, as (\ref{EQ:linear1}) - (\ref{EQ:linear3}) and their subsequent forms are linear with respect to the perturbations. 
For completeness, we provide the normalization 
\begin{equation}
    \int_{-\frac{1}{2}}^{\frac{1}{2}} \big| \theta (z) \big| dz = 1
\end{equation}
and assign each perturbation a yet-unknown amplitude $A \in \mathbb{R}$, thereby allowing us to reduce (\ref{EQ:T't_xz}) to the initial value problem (IVP)
\begin{equation}
    \frac{\partial \bar{T}}{\partial t} + A^2 \langle w'T' \rangle = \mathcal{P}  \frac{\partial^2 \bar{T}}{\partial z^2}, \label{EQ:T0_IVP}
\end{equation}
upon which the remainder of this investigation is centered. 
It is important to keep in mind that the forcing term $\langle w'T' \rangle$ is obtained by solving an eigenvalue problem (EVP) which itself involves $\frac{\partial \bar{T}}{\partial z}$. 
We also assume this term is composed of eigenfunctions belonging to the dominant mode. 
\par For various $Ra$ and fixed $Pr = 1$, we seek symmetric, marginally-stable temperature profiles $\bar{T}_{eq}(z)$ which are thermally equilibrated, thereby satisfying $\frac{\partial \bar{T}_{eq}}{\partial t} = 0$ according to (\ref{EQ:T0_IVP}). 
We employ the \texttt{Dedalus} pseudo-spectral python framework to solve the EVP outlined in Section \ref{sec:boussinesq} as well as the IVP (\ref{EQ:T0_IVP}) by representing each field with a dealiased Chebyshev polynomial basis. 
The necessary number of basis functions varies, as eigenfunctions and temperature profiles associated with large Rayleigh numbers admit increasingly small-scale features. 
We supplement \texttt{Dedalus} with the \texttt{Eigentools} package to obtain the eigenfunctions in (\ref{EQ:T0_IVP}).

To find an equilibrated profile, we begin with a marginally-stable initial profile $\bar{T}_0(z)$ whose construction is outlined in \ref{sec:initial_profile}. 
We seek to evolve $\bar{T}_0(z)$ into a new marginally-stable profile $\bar{T}_1(z)$ according to (\ref{EQ:T0_IVP}) using forward-Euler. 
This generally involves a unique and unknown value $A^2 > 0$. 
Our method of finding $A^2$ is best illustrated through example.

\begin{figure}
    \includegraphics[width=3.4in]{EV_spectrum_ol.png}
    \caption{Eigenvalue spectra for $Ra = 10^5$. The spectrum of a marginally-stable mean temperature profile $\bar{T}_0$ (shown in black) has a maximum eigenvalue of 0. 
    Given a small fixed timestep $\Delta t$, diffusion destabilizes the system, increasing its eigenvalues (shown in blue). 
    Advection tends to stabilize the system, decreasing its eigenvalues (shown in red). 
    It follows that there exists some proportion ($A^2$) of these two terms which yields a new marginally-stable mean temperature profile $\bar{T}_1$, whose spectrum is shown in green.}
    \label{fig:iteration_spectra} 
\end{figure}

@@

\section{Properties of Thermally Equilibrated States}\label{sec:properties}
Thermally equilibrated states of this kind are solutions to a particular quasilinear form of the Rayleigh-B\'enard convection equations. 
For this investigation, we calculate solutions for $Ra$ in the range $10^5 - 10^9$. 
Solutions are symmetric about $z = 0$ by construction. 
This, combined with the fact that we did initialize a mean horizontal flow implies the absence of any nonzero horizontal velocity perturbations, as is the case in \cite{Waleffe}.

Figure \ref{fig:T0_profiles} gives temperature profiles for $Ra = 10^8$ where the initial profile, given by (\ref{EQ:T0}), is employed at iteration 0; the equilibrated profile corresponds to the thermally relaxed state; and the simulation profile is obtained by performing a nonlinear simulation of (\ref{EQ:motion1})-(\ref{EQ:motion3}) with \texttt{Dedalus}, followed by horizontal and time averaging. 
The simulation curve is more diffuse than the equilibrated curve, which in turn, is more diffuse than the initial curve. 
Performing an eigenvalue solve by setting $\bar{T}$ equal to the simulation profile yields positive eigenvalues. 
Comprehensively, this suggests that thermally-equilibrated states might maximize boundary layer thickness, while subject to the marginal stability constraint.

The most resilient and unexpected feature of thermally equilibrated mean temperature profiles are the pronounced dips adjacent to the boundary layers. 
These dips appear in every solution, regardless of $Ra$. 
Physically, they correspond to thin layers in which the temperature gradient reverses, contradicting a hypothesis of \cite{Malkus}. 
This counter-diffusion, which opposes overall heat transfer, is overcome by the coinciding advective flux, shown in Figure \ref{fig:flux}. 
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{T_profs_na.png}
    \caption{mean temperature profiles $\bar{T}$ for $Ra = 10^8$. 
    The initial profile is given by (\ref{EQ:T0}). 
    The equilibrated curve refers to the mean temperature profile of the marginally-stable thermally-equilibrated state. 
    The simulation profile is obtained by performing a 2-dimensional nonlinear simulation with \texttt{Dedalus} until thermal and kinetic relaxation. 
    The simulation temperature data are horizontally- and time-averaged. 
    The initial, equilibrated, and simulation profiles have increasingly relaxed boundary regions (respectively). 
    The equilibrated profile exhibits prominent dips, nested alongside the boundary regions. 
    The purpose of this feature is not well understood.}
    \label{fig:T0_profiles}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=3.4in]{kx_m_ra1.png}
    \caption{Wavenumbers of marginally-stable modes of thermally equilibrated states. 
    Markers are color-coded according to their adjacent local maxima index in the eigenvalue spectrum. 
    For example, the spectrum corresponding to $Ra = 10^5$ has marginal wavenumbers $k_x = \pi, \, 1.5\pi$ adjacent to a presumed local maximum between these two allowed values. 
    The $Ra = 10^9$ spectrum, shown in lower right corner of Figure \ref{fig:flux}, has three presumed local maxima, with a single marginal mode adjacent to the first maximum ($k_x = 1.5\pi$), two marginal modes adjacent to the second maximum ($k_x = 6\pi, \, 6.5\pi$), and two marginal modes adjacent to the third maximum ($k_x = 23.5\pi, \, 24\pi$). 
    The largest wavenumbers of the green branch obey a power-law relationship with $Ra$}
    \label{fig:kx_marginals}
\end{figure}
\begin{figure*}
    \centering
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{flux_sup_n.png}
    \end{tabular}
    \begin{tabular}{@{}c@{}}
        \includegraphics[width=3.4in]{EV_spectra_2ra.png}
    \end{tabular}
    \caption{Heat fluxes (left) and eigenvalue spectra (right) of equilibrated states $Ra = 2 \times 10^5$ (top) and $Ra = 10^9$ (bottom). 
    Advection profiles belong to marginally-stable modes. 
    For low $Ra$, a single mode with $k_x = 1.5\pi$ is sufficient to oppose boundary layer diffusion and facilitate heat flux throughout the bulk of the domain. 
    For large $Ra$, high-wavenumber modes contribute pronounced small-scale advection profiles which tightly hug the thin boundary layers. 
    A combination of of progressively wider advection profiles is necessary to transition to the $k_x = 1.5\pi$ mode.}
    \label{fig:flux}
    \vspace{0.4in}
    \includegraphics[width=7.1in]{nu_ra.PNG}
    \caption{Nusselt numbers are shown for marginally-stable thermally-equilibrated states, statistically-steady direct numerical simulations performed with \texttt{Dedalus} \cite{Anders_cd}, and equilibrated nonlinear solutions, which maximize heat flux, given by \cite{Waleffe}. 
    Both obey power-law relationships with $Ra$, with $Ra \sim \Nu^3$ in agreement with Figures \ref{fig:bl_ra}, \ref{fig:kx_marginals}, and \ref{fig:del_inv} as well as \cite{Malkus}. 
    Marginally-stable states' Nusselt numbers exceed simulation Nusselt numbers. 
    This can be well explained by the contrasting boundary region geometries shown in Figure \ref{fig:T0_profiles}.}%
    \label{fig:nu_vs_ra}%
\end{figure*}

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_kx_inv.png}
    \caption{For $Ra \geq 10^6$, the maximum marginally-stable wavenumber (corresponding to the green X markers in Figure \ref{fig:kx_marginals}) are inversely related to the boundary layer thicknesses $\delta$. 
    $(\max \{ k_x \})^{-1}$ gives a minimum $x$ length scale for the perturbations, and consequently, the advection. 
    We expect the minimum $z$ length scale to agree with the boundary layer thickness $\delta$ because otherwise the boundary layer would continue to diffuse. 
    This is illustrated in the lower left corner of Figure \ref{fig:flux}, where the advection profile for $k_x = 24\pi$ is tightly flanked by the surrounding boundary layers. 
    This suggests that the minimum $x$ and $z$ length scales obey some constant ratio.}
    \label{fig:del_inv}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=3.4in]{del_ra.PNG}
    \caption{Boundary layer widths $\delta$ of marginally-stable thermal equilibria. 
    We define the threshold of each boundary layer as the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, corresponding to the local extrema of the equilibrated curve in Figure \ref{fig:T0_profiles}. 
    Plotting on a log-log scale, we find $\delta$ and $Ra$ obey a power-law relationship. We also demonstrate that $Ra^{1/3}\delta$ is approximately constant with respect to $Ra$ implying $Ra \propto  \delta^{-3}$, as predicted by \cite{Malkus}}
    \label{fig:bl_ra}
\end{figure}

@@

In general, marginally-stable thermal equilibria can be characterized by their boundary layer thicknesses, from which, the rest of their properties follow. Letting the interior boundary layer threshold be the $z$-coordinate at which $\frac{\partial \bar{T}}{\partial z} = 0$, we find that $Ra \propto  \delta^{-3}$ as illustrated in Figure \ref{fig:bl_ra}. 
This is consistent with Malkus' classical marginal-stability theory, a scaling argument which perceives the boundary regions as subdomains which are themselves marginally-stable.

@@

This investigation is partially motivated by the prospect of decreasing nonlinear simulation relaxation times by employing thermally-equilibrated initial conditions. 
Conventionally, (\ref{EQ:motion1}) - (\ref{EQ:motion3}) are solved via direct numerical simulation (DNS) with initial conditions

@@

which will hereby be referred to as the conductive initial condition. 
$t$ in this section now refers to the simulation time as opposed to the thermal equilibration time parameter used previously. 
We define the equilibrated initial conditions

@@

@@

\begin{figure}
    \begin{minipage}{3.4in}
